The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-02 manuscript.Rmd
updat preprint footer

# for submission to arXiv, copy the following files into a new folder and run pdfLaTeX directly on RJwrapper.tex (works with RStudio): figures/*, manuscript.tex, RJournal.sty, RJreferences.bib, RJwrapper.tex
# then zip the following files and submit to arXiv:
# - /figures
# - manuscript.tex
# - RJournal.sty
# - RJwrapper.bbl
# - RJwrapper.tex
```

>>>>

# For submission to arXiv:
# 1. Copy the following files into a new folder:
# - figures/*
# - manuscript.tex
# - RJournal.sty
# - RJreferences.bib
# - RJwrapper.tex
# 2. Run pdfLaTeX directly on RJwrapper.tex (works with RStudio)
# 3. Zip the following files and submit to arXiv:
# - /figures
# - manuscript.tex
# - RJournal.sty
# - RJwrapper.bbl
# - RJwrapper.tex
```
